\chapter{Conclusions}\label{chap:conclusions}

In this chapter we will review the general objectives of this dissertation. We will also recap the idea behind the proposed project, along with its implementation idealization. Lastly, we will give some perspective about future work.

\section{Objectives}

As stated before, our main objective for this dissertation is to implement a data analysis module that will apply data mining techniques to the information available (user actions captured via Selenium, HTML and URLs of each page visited, metrics) and so identify UI patterns in a Web aplication. The other major goals of this dissertation are extending the existent identification of patterns and implementing the prodution of a PARADIGM model for the PARADIGM-ME tool to process

\section{Project}

This project will be the materialization of the aforementioned objectives. As such, we will be adaptating the chosen learning algorithm, implement the identification of additional patterns, and implementing the model export module. At the end of the project it is expected to have a fully implemented pattern identifying tool, that hopefully identifies UI patterns more efficiently than the current work.

\section{Future Work}

The project will be implemented in three main phases. The first phase is the implementation of the objectives mentioned above. The other two phases are intensive testing of the resulting application and conducting experiments in learning Web applications, respectively. The results of the data analysis module will be compared with the current identifying heuristics to check if there have been improvements compared to the previous work.
